---
title: "xx"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(marginaleffects)


linear_reg(engine= "lm") |>fit(att_end ~ sex, data = trains)|>tidy(conf.int = TRUE)






```
$$
Y = \beta_0 + 
```{r}
#| cache: true
linear_reg(engine= "lm") |>fit(att_end ~ treatment, data = trains) 
```\beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_k X_k + \varepsilon
$$

## Fitted Model

$$
\hat{Y} = 5.2 - 0.8 \cdot \text{station}
$$


title: "Fitted Model Example"
format: html
---

## Fitted Model Table

```{r}
library(parsnip)
library(broom)
library(gt)

# Fit the model
fit_att <- linear_reg(engine= "lm") |> fit(att_end ~ treatment, data = trains)

# Tidy and display a formatted table
tidy(fit_att, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(term = recode(term,
                       "(Intercept)" = "Intercept",
                       "treatmentTreated" = "Treatment (Treated)")) |>
  gt() |>
  tab_header(
    title = "Regression Estimates with 95% Confidence Intervals"
  ) |>
  cols_label(
    term = "Term",
    estimate = "Estimate",
    conf.low = "95% CI Lower",
    conf.high = "95% CI Upper"
  ) |>
  fmt_number(columns = c(estimate, conf.low, conf.high), decimals = 2)

```



## Visualization of Treatment Effect

```{r}
library(ggplot2)
library(dplyr)

avg_comparisons(fit_att) |>
  ggplot(aes(x = 1, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  size = 1.2,
                  linewidth = 1.5,
                  color = "#2E86AB") +
  scale_y_continuous(breaks = seq(0, 3, 0.5), limits = c(0, 3)) +
  labs(
    title = "Causal Effect of Exposure to Spanish Speakers on Immigration Attitudes",
    subtitle = "Exposure to Spanish speakers leads to more positive views on immigration",
    caption = "Source: Enos (2012)",
    y = "Effect (on 3 to 15 Scale)",
    x = NULL
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 13),
    plot.caption = element_text(size = 10, color = "gray40"),
    axis.title.y = element_text(size = 12)
  )

```
```


We examine how exposure to Spanish speakers influences immigration attitudes among Georgia voters today, using insights from a 2012 experiment on Boston commuters.However, a potential weakness in our model is that the Boston sample may not be representative of Georgia voters, which could bias our estimates of the treatment effect.We model immigration attitudes—measured on a numerical scale—as a linear function of exposure to Spanish speakers, based on whether participants received the treatment or not.On average, exposure to Spanish speakers increases immigration attitude scores by 1.55 points, with a 95% confidence interval ranging from 0.51 to 2.58, indicating a statistically significant positive effect.